---
title: "Week 04 Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Exercises

```{r}
if(! require("pacman")) install.packages("pacman")

pacman::p_load(
  tidyverse,
  here
)
```

1. Read the `burritos.csv` file located in the `Data` folder into an object called `burritos`.

```{r}

```

2. Determine how many `NA` values exist in each column.

```{r}

```

3. Many of the columns in the dataset use `x` to indicate whether or not the burrito includes the ingredient or not. Convert these columns into logical columns. Overwrite the original dataframe with the newly mutated dataframe.

```{r}

```

4. For these same fields, determine how many burritos include each ingredient.

```{r}

```

5. Several of the burritos are missing Yelp and Google review values. Replace the missing values by imputing them with the *median* of their respective column. Overwrite the original dataframe with the newly mutated dataframe.

```{r}

```

6. Similarly, several of the burritos are missing `Length`, `Circum`, and `Volume` values. Replace the missing values by imputing them with the *mean* of their respective column. Overwrite the original dataframe with the newly mutated dataframe.

```{r}

```

7. The `Rec` column is messy. Convert it to a logical field. Overwrite the original dataframe with the newly mutated dataframe.

```{r}

```

8. Create and answer three questions to answer about the burritos dataset.

